Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions

### 2022-12-19 paper/new/article.tex
Work update

\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Ackley Function}
\label{fig:ackley}
\includegraphics[scale=0.5]{images/ackley.jpg}
\end{figure}
\subsection{Beale Function}
\label{beale2D}

@@

The Ackley function has a very large search space around the optimal solution and
it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
BFGS/LBFGS performed as expected.

@@

\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Beale Function}
\label{fig:beale}
\includegraphics[scale=0.5]{images/beale.jpg}
\end{figure}
\subsection{Booth Function}
\label{booth2D}

@@

\begin{table}[H]
\centering
\caption{Best Fits For Booth Function}
\label{solutions:booth}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      4 &        6 &      0.00 \\
 bfgs & $S_{2}$ &      2 &        5 &      0.00 \\
lbfgs & $S_{3}$ &      5 &       21 &      0.00 \\
  lma & $S_{4}$ &     10 &       11 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The isolines of Ackley Function and convergence lines for all algorithms are shown in Figure~\ref{fig:ackley}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Ackley Function}
\label{fig:ackley}
\includegraphics[scale=0.5]{images/ackley.jpg}
\end{figure}
The isolines for Ackley Function shows that there are at least 4 pitfalls near ther optimal solution, so, the search space needs to be reduced to \$[-0.05, 0.05]\$ to avoid wrong convergence. All the algorithms converges quite smoothly following a straight line\subsection{Beale Function}
\label{beale2D}

@@

The Beale function has a very large search space around the optimal solution and
it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
BFGS/LBFGS performed as expected.

@@

The isolines of Beale Function and convergence lines for all algorithms are shown i Figure~\ref{fig:beale}:\begin{figure}[H]
\centering
\caption{Isolines and convergence line for Beale Function}
\label{fig:beale}
\includegraphics[scale=0.5]{images/beale.jpg}
\end{figure}
The isolines for Beale Function shows that there are a large plateau near the solution. For an unknown reason the best algorithm had 80\% of performance at its best. Quasi-Newton algorithms suffers to converge when the gradient is less significant.\subsection{Booth Function}
\label{booth2D}

@@

The best solutions of all algorithms for Booth Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:booth}:
\begin{table}[H]
\centering
\caption{Best Fits For Booth Function}
\label{solutions:booth}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      4 &        6 &      0.00 \\
 bfgs & $S_{2}$ &      2 &        5 &      0.00 \\
lbfgs & $S_{3}$ &      5 &       21 &      0.00 \\
  lma & $S_{4}$ &     10 &       11 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}
